\documentclass{report}
	\author{Ding}
	\title{LEARNING NOTE}
	\usepackage{styles/zhfontcfg}
	%\usepackage{fontspec/fontspec}
	%\defaultfontfeatures{Mapping=tex-text}
\begin{document}
\maketitle

\begin{abstract}
\par中文
This is a learning note to record my process of learning this summar vacation. I started learning advance acknowledge from July 5th. Till Augest 28th I gotta have basically mastered the tools and the programming language as is mentioned in my report.\par
Actually, this is not only a vacation target. It's also a necessary process before being a Juvenior postgraduate, cause I have to do my opening report in the first term of Grade 2. That means I'm supposed to start from the firstyear and as earlier as possible.\par
Time's rushing. I'm gonna do my best and try hard all along.
\end{abstract}
\tableofcontents

\section{What I gotta learn}
	\paragraph{Ubuntu \\ Latex \\ GitHub \\ C++ \\ Python \\ 4 sections of Digital Image Processing}
\section{Ubuntu}
	\paragraph{Tasks}:\par
	1.recite the commands in common use.\par
	2.use it everyday!
	\paragraph{Sum up}:\par
	Ubuntu is an OS based on Linux. The word come from a language in south Africa. Here are some frequently-used command.
	\subparagraph{command}
	:\par
	man \(\):searching for help\par
	pwd: print working directory(Where I am)\par
	ls:list\par
	cd:change directory\par
	cp:copy\par
	mv:move\par
	rm:remove -r:remove means \par
	rmdir:remove directory\(it has to be empty\)\par
	mkdir:make directory\par
	All of these commands has different functions with different suffix
	such as "-r","-i","-l","-a"......:\par
	apt-get install...\par
	apt-get remove...\par
	apt-get remove --purge...:remove the app and files\par
	apt-get update...\par
	apt-cache search...\par
	dpkg -i xxx.deb:install\par
	dpkg -r xxx.deb:remove\par
	dpkg -r --purge xxx.deb:remove deb and files\par
	dpkg -L xxx.deb:get the details about file copying\par
	dpkg -info xxx.deb:get information of software package\par
	dpkg -l:get information about software packages that have been installed\par
	dpkg -reconfigure xxx\par
	\subparagraph{shortcut key}:\par
	ctrl+h: reveal the hidden files\par
	ctrl+f: search in this page\par
	ctrl+s: save\par
	ctrl+alt+t: call the terminal\par
	Find more at http://www.educity.cn/linux/660186.html
\section{Latex}
	\paragraph{Tasks}:\par
	1.recite the command in common use\par
	2.finish this report using texlive
	\paragraph{Sum up}:\par
	\subparagraph{Line and page}:\par
	Two backspace and $\backslash$par:start a new line with retract.\par
	$\backslash$$\backslash$ and $\backslash$newline: start a new line without retract. \par
	$\backslash$linebreak[n], $\backslash$nolinebreak[n], $\backslash$pagebreak[n], $\backslash$nopagebreak[n]: start a new page.\par
	\subparagraph{Special}:\par
	\# \$ \% \& \_ \{ \} $\backslash$\par
	\subparagraph{Font style}:\par
	$\backslash$textsl\{\textsl{lean}\}\par
	Actually, we can download template to lower working load. All you have to do is change the words in it!
\section{GitHub}
	\paragraph{Sum up}:\par
	GitHub is a platform for personal users to pull their own code and download others code freely. We can easily manage code we write ourselves and Github has a large mount of source that we can also easily find what we want.\par
	Now let's describe it more professional.Git is a distributed version control system\(DRCS\),originally written by linus Torvalds to manage the source code of the Linux kernel. And the advantage of the system is that it copies the entire virtual warehouse. So that whichever server break down, it can call the replication and recover the inaccuracy code. Besides, everytime a server do a submit there will generate a new replication. That means you can easily regain your code no matter when it was compiled. It's really convenience!\par 
	P.S. Found an interestion website just like GitHub named "mayun".Differently, it's Chinese!
	\subparagraph{operation method}:\par
	set up a new file: touch FILE\par
	write content: vim FILE\par
	check the state: git status\par
	trace the file: git add FILE\par
	cancel the trace: git rm --cached FILE\par
	commit the file: git commit -m 'message'\par
	commit immediately: git commit -a -m 'message'\par
	check commit history: git log$\sim$ -p:see the difference -2: see the latest two renew
\section{OpenCV}
	\paragraph{Sum up}:\par	
	C++, as far as I'm concerned,is familiar with C but better. It provides better type check and compiling analyse, and it's safer than C. Since C++ is compatible with C, most code written in C can directely operating in C++. Besides, C++ is more friendly. We can easily understand it's thought.\par
	basic start:\par
	\(\#include <opencv/core/core.hpp>\)\par
	\(\#include <opencv2/highgui/haigui.hpp>\)\par 
	\(using namespace cv\)\par
	Find more at http://blog.csdn.net/poem\_qianmo/article details/20537737
\section{Python}
	\paragraph{Sum up}:\par
	Python is even easier to learn than C++. The main difference is that Python is refined, decreased unwanted parts so that Python runs a lot faster than C. On the other side, C++ can realize more function sometimes. 
\section{4 sections of Digital Image Processing}
	\paragraph{Tasks}:\par 
	1.Take notes in detail.\par 
	2.compile part histogram and part smoothing using C++
\end{document}
